Dealing with Consumer Uncertainty: Online Consumer Reviews and What makes them helpful?

### 2022-11-02 Paper.Rmd
numerous additions
good usage of comments very nice bruh

Online shopping has becoming more and more prevalent in average consumer's daily life. Electronic shopping brought many advantages both for sellers and buyers. One of the positive perks is Online Customer Reviews (OCR). Online Customer Reviews come in the form of electronic word-of-mouth [@dellarocas2003] and can be defined as "*peer-generated product evaluations posted on company or third party websites*" [@mudambi2010]. OCR have an effect on product sales as well as consumer decision making [@duan2008; @lee2011; @dellarocas2007].

@@

The research on Online Customer Reviews could be considered to have two main branches. One branch is heavily marketing oriented and tries to understand the effects of OCR on sales [@ghose2011; @ögüt2012]. The other branch is concerned with rather behavioral or psychological outcomes and focuses on perceived helpfulness only. The boundary between these two branches are somewhat blurry and the same independent variables were used to explain both helpfulness and sales. Furthermore, @topaloglu2019 found that helpfulness have a moderating effect on sales. Many other papers used perceived helpfulness to explain sales as well [@ghose2011; @lee2018]. Thus, these two branches are inter-connected with each other. This paper tries to understand behavioral aspect of the review helpfulness rather than its effects on sales.

@@

Online Customer Reviews from IMDB were collected as an experience goods data since movies can be considered as pure-experience goods and their search attributes are very limited. It is nearly impossible to evaluate a movie before watching it. Furthermore, evaluations for a movie can both have subjective (personal attachment to the protagonist, atmosphere of the movie etc.) and objective aspects (writing, production quality etc.). There are also numerous studies that analyzed movies as experience goods[@nelson1970; @liu2014; @ghose2006; @baek2012; @lee2016].

@@

search_goods %>% 
  ggplot(aes(Helpfulness))+
  geom_histogram(color = "white", fill = "steelblue", boundary = 0)+
  scale_x_continuous(n.breaks = 10)+
  labs(y = "Count")

@@

```{r IV-Hist-Exp, fig.cap="Distribution of the Helpfulness of Experience Goods"}
movies_data %>% 
  ggplot(aes(Helpfulness))+
  geom_histogram(color = "white", fill = "steelblue", boundary = 0)+
  scale_x_continuous(n.breaks = 10)+
  labs(y = "Count")
```

@@

```{r Search-Rating, fig.cap="The Distribution(A) and the Scatter Plot(B) of Review Rating for Search Goods."}
p1 <- search_goods %>% 
  ggplot(aes(Rating))+
  geom_bar(fill = "steelblue")+
  labs(y = "Count", x = "Review Rating")

@@

```{r Experience-Rating, fig.cap="The Distribution(A) and the Scatter Plot(B) of Review Rating for Experience Goods."}
p1 <- movies_data %>% 
  ggplot(aes(Rating))+
  geom_bar(fill = "steelblue")+
  scale_x_continuous(n.breaks = 10)+
  labs(y = "Count", x = "Review Rating")

@@

```{r Search-Length, fig.height=6, fig.cap="The Distribution(A) and the Scatter Plot(C) of Review Length for Search Goods and respective logarithmic transformations (B), (D)"}
p1 <- search_goods %>% 
  ggplot(aes(Word_Count))+
  geom_histogram(color = "white", fill = "steelblue", boundary = 0)+
  scale_x_continuous(n.breaks = 8)+
  labs(y = "Count", x = "Number of the Words")

p1_log <- search_goods %>% 
  ggplot(aes(Word_Count))+
  geom_histogram(color = "white", fill = "steelblue", boundary = 10)+
  scale_x_log10(n.break = 8)+
  labs(y = "Count", x = "log10(Number of the Words)")

@@

```{r Experience-Length, fig.height=6, fig.cap="The Distribution(A) and the Scatter Plot(C) of Review Length for Experience Goods and respective logarithmic transformations (B), (D)"}
p1 <- movies_data %>% 
  ggplot(aes(Word_Count))+
  geom_histogram(color = "white", fill = "steelblue", boundary = 0)+
  scale_x_continuous(n.breaks = 7)+
  labs(y = "Count", x = "Number of the Words")

p1_log <- movies_data %>% 
  ggplot(aes(Word_Count))+
  geom_histogram(color = "white", fill = "steelblue", boundary = 10)+
  scale_x_log10(n.break = 7)+
  labs(y = "Count", x = "log10(Number of the Words)")

@@

```{r Search-Freshness, fig.height=6, fig.cap="The Distribution(A) and the Scatter Plot(C) of Review Freshness for Search Goods and respective logarithmic transformations (B), (D)"}
p1 <- search_goods %>% 
  ggplot(aes(Freshness))+
  geom_histogram(color = "white", fill = "steelblue", boundary = 0)+
  scale_x_continuous(n.breaks = 7)+
  labs(y = "Count", x = "Freshness of Review")

p1_log <- search_goods %>% 
  ggplot(aes(Freshness + 1))+
  geom_histogram(color = "white", fill = "steelblue", boundary = 10)+
  scale_x_log10(n.break = 7)+
  labs(y = "Count", x = "log10(Freshness of Review + 1)")

@@

```{r Experience-Freshness, fig.height=6, fig.cap="The Distribution(A) and the Scatter Plot(C) of Review Freshness for Experience Goods and respective logarithmic transformations (B), (D)"}
p1 <- movies_data %>% 
  ggplot(aes(Freshness))+
  geom_histogram(color = "white", fill = "steelblue", boundary = 0)+
  scale_x_continuous(n.breaks = 6)+
  labs(y = "Count", x = "Freshness of Review")

p1_log <- movies_data %>% 
  ggplot(aes(Freshness + 1))+
  geom_histogram(color = "white", fill = "steelblue", boundary = 1)+
  scale_x_log10(n.break = 6)+
  labs(y = "Count", x = "log10(Freshness of Review + 1)")

@@

```{r Search-Neg, fig.cap="The Distribution(A) and the Scatter Plot(B) of Proportion of Negative Words for Search Goods"}
p1 <- search_goods %>% 
  ggplot(aes(negative))+
  geom_histogram(color = "white", fill = "steelblue", boundary = 0)+
  scale_x_continuous(n.breaks = 8)+
  labs(y = "Count", x = "Log10(Proportion of Negative Words)")

@@

```{r Experience-Neg, fig.cap="The Distribution(A) and the Scatter Plot(B) of Proportion of Negative Words for Experience Goods"}
p1 <- movies_data %>% 
  ggplot(aes(negative))+
  geom_histogram(color = "white", fill = "steelblue", boundary = 0)+
  scale_x_continuous(n.breaks = 8)+
  labs(y = "Count", x = "Log10(Proportion of Negative Words)")

@@

```{r Search-Pos, fig.cap="The Distribution(A) and the Scatter Plot(B) of Proportion of Positive Words for Search Goods"}
p1 <- search_goods %>% 
  ggplot(aes(positive))+
  geom_histogram(color = "white", fill = "steelblue", boundary = 0)+
  scale_x_continuous(n.breaks = 8)+
  labs(y = "Count", x = "Log10(Proportion of Positive Words)")

@@

```{r Experience-Pos, fig.cap="The Distribution(A) and the Scatter Plot(B) of Proportion of Positive Words for Experience Goods"}
p1 <- movies_data %>% 
  ggplot(aes(positive))+
  geom_histogram(color = "white", fill = "steelblue", boundary = 0)+
  scale_x_continuous(n.breaks = 8)+
  labs(y = "Count", x = "Log10(Proportion of Positive Words)")

@@

```{r Search-Total, fig.height=6, fig.cap="The Distribution(A) and the Scatter Plot(C) of Total Votes for Search Goods and respective logarithmic transformations (B), (D)"}
p1 <- search_goods %>% 
  ggplot(aes(Total_Vote))+
  geom_histogram(color = "white", fill = "steelblue", boundary = 0)+
  scale_x_continuous(n.breaks = 7)+
  labs(y = "Count", x = "Total Vote")

p1_log <- search_goods %>% 
  ggplot(aes(Total_Vote))+
  geom_histogram(color = "white", fill = "steelblue", boundary = 10)+
  scale_x_log10(n.break = 7)+
  labs(y = "Count", x = "log10(Total Vote)")

@@

```{r Experience-Total, fig.height=6, fig.cap="The Distribution(A) and the Scatter Plot(C) of Total Votes for Experience Goods and respective logarithmic transformations (B), (D)"}
p1 <- movies_data %>% 
  ggplot(aes(Total_Vote))+
  geom_histogram(color = "white", fill = "steelblue", boundary = 0)+
  scale_x_continuous(n.breaks = 7)+
  labs(y = "Count", x = "Total Vote")

p1_log <- movies_data %>% 
  ggplot(aes(Total_Vote))+
  geom_histogram(color = "white", fill = "steelblue", boundary = 1)+
  scale_x_log10(n.break = 6)+
  labs(y = "Count", x = "log10(Total Vote)")

@@

This study collected Online Customer Reviews data from two different sources (IMDB and BestBuy) and analyzed the data within the context of consumer uncertainty. Negativity Bias Theorem, Prospect Theory and Search / Experience goods paradigm from information economics were used as theoretical engines to explain the information gathering process of an average consumer. Results showed similarities from the existing Review Helpfulness literature. However, once again it should be noted that the literature has many conflicting results.

@@

There are some implications for future studies. Firstly, aside from lexicon based sentiment analysis it is also possible to utilize deep learning methods to mine opinions from a text. One advantage of deep learning method over a lexicon is its versatility. A negative word can change from one context to another and training a deep learning method is more robust to this type of contextual changes whereas with lexicon based methods a negative word is a negative word no matter the context is. Next, future studies should consider collecting data from different regions and cultures. There might be some differences on how consumers process and react to the information in order to deal with uncertainty. Additionally, researchers can dig deeper into search and experience goods paradigm. It is well established in the literature that product type affects the information gathering process. However, there might be differences within product types depending on their search and experience attributes. An objective way to identify and index experience and search attributes may also shed some light to the conflicting results in the literature. Lastly, since Online Customer Reviews data is ever growing more researchers should incorporate Exploratory Data Analysis into their works. Reviews and how helpful these reviews are perceived by potential buyers is relatively a new topic. In addition, new ways to analyze text data are being developed so Online Customer Reviews offer a great potential for new discoveries from the data. This increases the value of EDA as well.

>>>>

Online shopping has becoming more and more prevalent in average consumer's daily life. Electronic shopping brought many advantages both for sellers and buyers. One of the positive perks is Online Consumer Reviews (OCR). Online Consumer Reviews come in the form of electronic word-of-mouth [@dellarocas2003] and can be defined as "*peer-generated product evaluations posted on company or third party websites*" [@mudambi2010]. OCR have an effect on product sales as well as consumer decision making [@duan2008; @lee2011; @dellarocas2007].

@@

The research on Online Consumer Reviews could be considered to have two main branches. One branch is heavily marketing oriented and tries to understand the effects of OCR on sales [@ghose2011; @ögüt2012]. The other branch is concerned with rather behavioral or psychological outcomes and focuses on perceived helpfulness only. The boundary between these two branches are somewhat blurry and the same independent variables were used to explain both helpfulness and sales. Furthermore, @topaloglu2019 found that helpfulness have a moderating effect on sales. Many other papers used perceived helpfulness to explain sales as well [@ghose2011; @lee2018]. Thus, these two branches are inter-connected with each other. This paper tries to understand behavioral aspect of the review helpfulness rather than its effects on sales.

@@

Online Consumer Reviews from IMDB were collected as an experience goods data since movies can be considered as pure-experience goods and their search attributes are very limited. It is nearly impossible to evaluate a movie before watching it. Furthermore, evaluations for a movie can both have subjective (personal attachment to the protagonist, atmosphere of the movie etc.) and objective aspects (writing, production quality etc.). There are also numerous studies that analyzed movies as experience goods[@nelson1970; @liu2014; @ghose2006; @baek2012; @lee2016].

@@

search_goods %>% 
  ggplot(aes(Helpfulness))+
  geom_histogram(color = "white", fill = "steelblue", boundary = 0)+
  geom_vline(aes(xintercept = mean(Helpfulness)), size = 1, alpha = 0.6)+
  annotate(geom = "label",
           x = mean(search_goods$Helpfulness), y = Inf,
           label = paste("Mean:", round(mean(search_goods$Helpfulness), digits = 2)),
           vjust = 1, hjust = 1, size = 5)+
  scale_x_continuous(n.breaks = 10)+
  labs(y = "Count")

@@

```{r IV-Hist-Exp, fig.cap="Distribution of the Helpfulness of Experience Goods"}

movies_data %>% 
  ggplot(aes(Helpfulness))+
  geom_histogram(color = "white", fill = "steelblue", boundary = 0)+
  geom_vline(aes(xintercept = mean(Helpfulness)), size = 1, alpha = 0.6)+
  annotate(geom = "label",
           x = mean(movies_data$Helpfulness), y = Inf,
           label = paste("Mean:", round(mean(movies_data$Helpfulness), digits = 2)),
           vjust = 1, hjust = 1, size = 5)+
  scale_x_continuous(n.breaks = 10)+
  labs(y = "Count")
```

@@

```{r Search-Rating, fig.cap="The Distribution(A) and the Scatter Plot(B) of Review Rating for Search Goods."}
p1 <- search_goods %>% 
  ggplot(aes(Rating))+
  geom_bar(fill = "steelblue")+
  geom_vline(aes(xintercept = mean(Rating)), size = 1, alpha = 0.6)+
  annotate(geom = "label", x = mean(search_goods$Rating), y = Inf, 
           label = paste("Mean:", round(mean(search_goods$Rating), digits = 2)),
           vjust = 1, hjust = 1, size = 4.5)+
  labs(y = "Count", x = "Review Rating")

@@

```{r Experience-Rating, fig.cap="The Distribution(A) and the Scatter Plot(B) of Review Rating for Experience Goods."}
p1 <- movies_data %>% 
  ggplot(aes(Rating))+
  geom_bar(fill = "steelblue")+
  geom_vline(aes(xintercept = mean(Rating)), size = 1, alpha = 0.6)+
  annotate(geom = "label", x = mean(movies_data$Rating), y = Inf, 
           label = paste("Mean:", round(mean(movies_data$Rating), digits = 2)),
           vjust = 1, hjust = 1, size = 4.5)+
  scale_x_continuous(n.breaks = 10)+
  labs(y = "Count", x = "Review Rating")

@@

```{r Search-Length, fig.height=6, fig.cap="The Distribution(A) and the Scatter Plot(C) of Review Length for Search Goods and respective logarithmic transformations (B), (D)"}
p1 <- search_goods %>% 
  ggplot(aes(Word_Count))+
  geom_histogram(color = "white", fill = "steelblue", boundary = 0)+
  geom_vline(aes(xintercept = mean(Word_Count)), size = 1, alpha = 0.6)+
  annotate(geom = "label", x = mean(search_goods$Word_Count), y = Inf, 
           label = paste("Mean:", round(mean(search_goods$Word_Count), digits = 0)),
           vjust = 1, hjust = 0, size = 4.5)+
  scale_x_continuous(n.breaks = 8)+
  labs(y = "Count", x = "Number of the Words")

p1_log <- search_goods %>% 
  ggplot(aes(Word_Count))+
  geom_histogram(color = "white", fill = "steelblue", boundary = 10)+
  geom_vline(aes(xintercept = mean(Word_Count)), size = 1, alpha = 0.6)+
  annotate(geom = "label", x = mean(search_goods$Word_Count), y = Inf, 
           label = paste("Mean:", round(mean(search_goods$Word_Count), digits = 0)),
           vjust = 1, hjust = 0, size = 4.5)+
  scale_x_log10(n.break = 8)+
  labs(y = "Count", x = "log10(Number of the Words)")

@@

```{r Experience-Length, fig.height=6, fig.cap="The Distribution(A) and the Scatter Plot(C) of Review Length for Experience Goods and respective logarithmic transformations (B), (D)"}
p1 <- movies_data %>% 
  ggplot(aes(Word_Count))+
  geom_histogram(color = "white", fill = "steelblue", boundary = 0)+
  geom_vline(aes(xintercept = mean(Word_Count)), size = 1, alpha = 0.6)+
  annotate(geom = "label", x = mean(movies_data$Word_Count), y = Inf, 
           label = paste("Mean:", round(mean(movies_data$Word_Count), digits = 0)),
           vjust = 1, hjust = 0, size = 4.5)+
  scale_x_continuous(n.breaks = 7)+
  labs(y = "Count", x = "Number of the Words")

p1_log <- movies_data %>% 
  ggplot(aes(Word_Count))+
  geom_histogram(color = "white", fill = "steelblue", boundary = 10)+
  geom_vline(aes(xintercept = mean(Word_Count)), size = 1, alpha = 0.6)+
  annotate(geom = "label", x = mean(movies_data$Word_Count), y = Inf, 
           label = paste("Mean:", round(mean(movies_data$Word_Count), digits = 0)),
           vjust = 1, hjust = 0, size = 4.5)+
  scale_x_log10(n.break = 7)+
  labs(y = "Count", x = "log10(Number of the Words)")

@@

```{r Search-Freshness, fig.height=6, fig.cap="The Distribution(A) and the Scatter Plot(C) of Review Freshness for Search Goods and respective logarithmic transformations (B), (D)"}
p1 <- search_goods %>% 
  ggplot(aes(Freshness))+
  geom_histogram(color = "white", fill = "steelblue", boundary = 0)+
  geom_vline(aes(xintercept = mean(Freshness)), size = 1, alpha = 0.6)+
  annotate(geom = "label", x = mean(search_goods$Freshness), y = Inf, 
           label = paste("Mean:", round(mean(search_goods$Freshness), digits = 0)),
           vjust = 1, hjust = 0, size = 4.5)+
  scale_x_continuous(n.breaks = 7)+
  labs(y = "Count", x = "Freshness of Review")

p1_log <- search_goods %>% 
  ggplot(aes(Freshness + 1))+
  geom_histogram(color = "white", fill = "steelblue", boundary = 10)+
  geom_vline(aes(xintercept = mean(Freshness)), size = 1, alpha = 0.6)+
  annotate(geom = "label", x = mean(search_goods$Freshness), y = Inf, 
           label = paste("Mean:", round(mean(search_goods$Freshness), digits = 0)),
           vjust = 1, hjust = 0, size = 4.5)+
  scale_x_log10(n.break = 7)+
  labs(y = "Count", x = "log10(Freshness of Review + 1)")

@@

```{r Experience-Freshness, fig.height=6, fig.cap="The Distribution(A) and the Scatter Plot(C) of Review Freshness for Experience Goods and respective logarithmic transformations (B), (D)"}
p1 <- movies_data %>% 
  ggplot(aes(Freshness))+
  geom_histogram(color = "white", fill = "steelblue", boundary = 0)+
  geom_vline(aes(xintercept = mean(Freshness)), size = 1, alpha = 0.6)+
  annotate(geom = "label", x = mean(movies_data$Freshness), y = Inf, 
           label = paste("Mean:", round(mean(movies_data$Freshness), digits = 0)),
           vjust = 1, hjust = 0, size = 4.5)+
  scale_x_continuous(n.breaks = 6)+
  labs(y = "Count", x = "Freshness of Review")

p1_log <- movies_data %>% 
  ggplot(aes(Freshness + 1))+
  geom_histogram(color = "white", fill = "steelblue", boundary = 1)+
  geom_vline(aes(xintercept = mean(Freshness)), size = 1, alpha = 0.6)+
  annotate(geom = "label", x = mean(movies_data$Freshness), y = Inf, 
           label = paste("Mean:", round(mean(movies_data$Freshness), digits = 0)),
           vjust = 1, hjust = 0, size = 4.5)+
  scale_x_log10(n.break = 6)+
  labs(y = "Count", x = "log10(Freshness of Review + 1)")

@@

```{r Search-Neg, fig.cap="The Distribution(A) and the Scatter Plot(B) of Proportion of Negative Words for Search Goods"}
p1 <- search_goods %>% 
  ggplot(aes(negative))+
  geom_histogram(color = "white", fill = "steelblue", boundary = 0)+
  geom_vline(aes(xintercept = mean(negative)), size = 1, alpha = 0.6)+
  annotate(geom = "label", x = mean(search_goods$negative), y = Inf, 
           label = paste("Mean:", round(mean(search_goods$negative), digits = 2)),
           vjust = 1, hjust = 0, size = 4.5)+
  scale_x_continuous(n.breaks = 8)+
  labs(y = "Count", x = "Log10(Proportion of Negative Words)")

@@

```{r Experience-Neg, fig.cap="The Distribution(A) and the Scatter Plot(B) of Proportion of Negative Words for Experience Goods"}
p1 <- movies_data %>% 
  ggplot(aes(negative))+
  geom_histogram(color = "white", fill = "steelblue", boundary = 0)+
  geom_vline(aes(xintercept = mean(negative)), size = 1, alpha = 0.6)+
  annotate(geom = "label", x = mean(movies_data$negative), y = Inf, 
           label = paste("Mean:", round(mean(movies_data$negative), digits = 2)),
           vjust = 1, hjust = 0, size = 4.5)+
  scale_x_continuous(n.breaks = 8)+
  labs(y = "Count", x = "Log10(Proportion of Negative Words)")

@@

```{r Search-Pos, fig.cap="The Distribution(A) and the Scatter Plot(B) of Proportion of Positive Words for Search Goods"}
p1 <- search_goods %>% 
  ggplot(aes(positive))+
  geom_histogram(color = "white", fill = "steelblue", boundary = 0)+
  geom_vline(aes(xintercept = mean(positive)), size = 1, alpha = 0.6)+
  annotate(geom = "label", x = mean(search_goods$positive), y = Inf, 
           label = paste("Mean:", round(mean(search_goods$positive), digits = 2)),
           vjust = 1, hjust = 0, size = 4.5)+
  scale_x_continuous(n.breaks = 8)+
  labs(y = "Count", x = "Log10(Proportion of Positive Words)")

@@

```{r Experience-Pos, fig.cap="The Distribution(A) and the Scatter Plot(B) of Proportion of Positive Words for Experience Goods"}
p1 <- movies_data %>% 
  ggplot(aes(positive))+
  geom_histogram(color = "white", fill = "steelblue", boundary = 0)+
  geom_vline(aes(xintercept = mean(positive)), size = 1, alpha = 0.6)+
  annotate(geom = "label", x = mean(movies_data$positive), y = Inf, 
           label = paste("Mean:", round(mean(movies_data$positive), digits = 2)),
           vjust = 1, hjust = 0, size = 4.5)+
  scale_x_continuous(n.breaks = 8)+
  labs(y = "Count", x = "Log10(Proportion of Positive Words)")

@@

```{r Search-Total, fig.height=6, fig.cap="The Distribution(A) and the Scatter Plot(C) of Total Votes for Search Goods and respective logarithmic transformations (B), (D)"}
p1 <- search_goods %>% 
  ggplot(aes(Total_Vote))+
  geom_histogram(color = "white", fill = "steelblue", boundary = 0)+
  geom_vline(aes(xintercept = mean(Total_Vote)), size = 1, alpha = 0.6)+
  annotate(geom = "label", x = mean(search_goods$Total_Vote), y = Inf, 
           label = paste("Mean:", round(mean(search_goods$Total_Vote), digits = 2)),
           vjust = 1, hjust = 0, size = 4.5)+
  scale_x_continuous(n.breaks = 7)+
  labs(y = "Count", x = "Total Vote")

p1_log <- search_goods %>% 
  ggplot(aes(Total_Vote))+
  geom_histogram(color = "white", fill = "steelblue", boundary = 10)+
  geom_vline(aes(xintercept = mean(Total_Vote)), size = 1, alpha = 0.6)+
  annotate(geom = "label", x = mean(search_goods$Total_Vote), y = Inf, 
           label = paste("Mean:", round(mean(search_goods$Total_Vote), digits = 2)),
           vjust = 1, hjust = 0, size = 4.5)+
  scale_x_log10(n.break = 7)+
  labs(y = "Count", x = "log10(Total Vote)")

@@

```{r Experience-Total, fig.height=6, fig.cap="The Distribution(A) and the Scatter Plot(C) of Total Votes for Experience Goods and respective logarithmic transformations (B), (D)"}
p1 <- movies_data %>% 
  ggplot(aes(Total_Vote))+
  geom_histogram(color = "white", fill = "steelblue", boundary = 0)+
  geom_vline(aes(xintercept = mean(Total_Vote)), size = 1, alpha = 0.6)+
  annotate(geom = "label", x = mean(movies_data$Total_Vote), y = Inf, 
           label = paste("Mean:", round(mean(movies_data$Total_Vote), digits = 2)),
           vjust = 1, hjust = 0, size = 4.5)+
  scale_x_continuous(n.breaks = 7)+
  labs(y = "Count", x = "Total Vote")

p1_log <- movies_data %>% 
  ggplot(aes(Total_Vote))+
  geom_histogram(color = "white", fill = "steelblue", boundary = 1)+
  geom_vline(aes(xintercept = mean(Total_Vote)), size = 1, alpha = 0.6)+
  annotate(geom = "label", x = mean(movies_data$Total_Vote), y = Inf, 
           label = paste("Mean:", round(mean(movies_data$Total_Vote), digits = 2)),
           vjust = 1, hjust = 0, size = 4.5)+
  scale_x_log10(n.break = 6)+
  labs(y = "Count", x = "log10(Total Vote)")

@@

This study collected Online Consumer Reviews data from two different sources (IMDB and BestBuy) and analyzed the data within the context of consumer uncertainty. Negativity Bias Theorem, Prospect Theory and Search / Experience goods paradigm from information economics were used as theoretical engines to explain the information gathering process of an average consumer. Results showed similarities from the existing Review Helpfulness literature. However, once again it should be noted that the literature has many conflicting results.

@@

There are some implications for future studies. Firstly, aside from lexicon based sentiment analysis it is also possible to utilize deep learning methods to mine opinions from a text. One advantage of deep learning method over a lexicon is its versatility. A negative word can change from one context to another and training a deep learning method is more robust to this type of contextual changes whereas with lexicon based methods a negative word is a negative word no matter the context is. Next, future studies should consider collecting data from different regions and cultures. There might be some differences on how consumers process and react to the information in order to deal with uncertainty. Additionally, researchers can dig deeper into search and experience goods paradigm. It is well established in the literature that product type affects the information gathering process. However, there might be differences within product types depending on their search and experience attributes. An objective way to identify and index experience and search attributes may also shed some light to the conflicting results in the literature. Lastly, since Online Consumer Reviews data is ever growing more researchers should incorporate Exploratory Data Analysis into their works. Reviews and how helpful these reviews are perceived by potential buyers is relatively a new topic. In addition, new ways to analyze text data are being developed so Online Consumer Reviews offer a great potential for new discoveries from the data. This increases the value of EDA as well.
